Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-06 paper/disc20clustering.tex
wip

@@

First, we construct a ground set of size $k-1$ on an arbitrary cluster $S$.
In any configuration, there exists an alone node on $S$.
We issue requests between the current alone node from $S$, and some node that was initially collocated with it.
Repeating such requests, almost all the nodes must visit the cluster $S$.
In comparison, \OPT performs one migration.

@@

\noindent
\textbf{Resource augmentation.}
The majority of work on Online Balanced Partitioning so far (todo: cite) focuses on the scenario with resource augmentation.
We note that this lower bound provides insights into this scenario as well.

Consider an instance with $k$ divisible by $3$, and construct $3$ ground sets of size $k/3$ in each cluster.
Then, apply the construction from the lower bound for $k=3$, now treating these ground sets in the way we used individual nodes.
For the resource augmentation as large as $1+1/3-\epsilon$, no more than $3$ such ground sets fit in one cluster.
The cost of any algorithm (including \OPT) scales up by $k/3$, and the lower bound $\Omega(\ell)$ holds.

Finally, we note the possibility for improvement (a gap). The algorithm CREP~\cite{repartition-disc} requires $(2+\epsilon)$-augmentation to guarantee the competitive ratio independent of $\ell$.

>>>>

\maciek{TODOs: "requests between nodes" to "requests to pair of nodes"}

@@

First, we construct a ground set of size $k-1$ on an arbitrary cluster $S$.
In any configuration, there exists an alone node on $S$.
We issue requests between the current alone node from $S$, and some node that was initially collocated with it.
Repeating such requests, almost all the nodes must visit the cluster $S$.
In comparison, \OPT performs only two migrations.

@@

\noindent
\textbf{Resource augmentation.}
The majority of work on Online Balanced Partitioning so far \cite{repartition-disc,sigmetrics19_partitioning} focuses on the scenario with resource augmentation, where the clusters of \ALG are larger than the clusters of \OPT.
We can adjust our construction to show a lower bound of $\Omega(\ell)$ for resource augmentation.

Consider a partitioning problem with resource augmentation $1+1/3-\epsilon$.
Fix $k$ divisible by $3$, and construct $3$ ground sets of size $k/3$ in each cluster.
Note that no more than $3$ such ground sets fit in one cluster.
Then, apply the construction from the lower bound for $k=3$, using these ground sets in the way we used individual nodes.
The cost of any algorithm (including \OPT) scales up by $k/3$, and the lower bound $\Omega(\ell)$ holds.

Finally, we note the possibility for improvement. The algorithm CREP~\cite{repartition-disc} requires $(2+\epsilon)$-augmentation to guarantee the competitive ratio independent of $\ell$.
